---
title: "R - PS4"
author: "Lingzhi Huang"
date: "4/22/2020"
output: html_document
---

```{r, message=FALSE}

library(rio)
library(tidyverse)
library(knitr)
```
```{r}
basic<- import('basic.dta')
genold<- import('genold108.dta')
```

```{r}
basic108th <- subset(basic, basic$congress==108,)
```

```{r, message=FALSE}
Combinedtable <- inner_join(genold,basic108th, by='name')
print(Combinedtable)
```
```{r}
Combinedtable <- Combinedtable[,c('name','genold','party','ngirls','nboys','totchi','rgroup','region','repub','srvlng','female','white','age')]
print(Combinedtable)
```

```{r}
Combinedtable$genold <- as.factor(Combinedtable$genold)
Combinedtable$genold[Combinedtable$genold == ''] <- NA
print(Combinedtable)
```

```{r}
Combinedtable$party <- factor(Combinedtable$party, levels = c(1,2,3), labels=c("D", "R", "I"))
Combinedtable$rgroup <- factor(Combinedtable$rgroup)
Combinedtable$region <- factor(Combinedtable$region)
print(Combinedtable)
```

generate variables for age squared and service length squared
```{r}
Agesqr <- Combinedtable$age^2
Srvlngsqr=Combinedtable$srvlng ^2
Combinedtable%>% mutate(Agesqr) %>%
  mutate(Srvlngsqr)
```
create an additional variable of the number of children as factor variable
```{r}
factor_totchi<- as.factor(Combinedtable$totchi)
```

# Replicating Table 1 from the Appendix
regression on number of daughters
```{r}
lm1 <- lm(ngirls~ genold + white + party +female+age + Agesqr + srvlng+ Srvlngsqr+ rgroup+ region, data = Combinedtable)
```

Save the main coefficient of interest
```{r}
coelm1<- summary(lm1)$coefficients[2,]
print(coelm1)
```

regression on number of children
```{r}
lm2 <- lm(totchi~ genold + white + party +female+age + Agesqr + srvlng+ Srvlngsqr+ rgroup+ region, data = Combinedtable)
```

Save the main coefficient of interest
```{r}
coelm2<- summary(lm2)$coefficients[2,]
print(coelm2)
```
Run the same regression separately for Democrats and Republicans (assign the independent to one of the parties). Save the coefficient and standard error of *genold*
```{r}
lm3 <- lm(ngirls~ genold + white + party +female+age + Agesqr + srvlng+ Srvlngsqr+ rgroup+ region, data = Combinedtable[Combinedtable$repub==1,])
coelm3<- summary(lm3)$coefficients[2,]
print(coelm3)

lm4 <- lm(totchi~ genold + white + party +female+age + Agesqr + srvlng+ Srvlngsqr+ rgroup+ region, data = Combinedtable[Combinedtable$repub==1,])
coelm4<- summary(lm4)$coefficients[2,]
print(coelm4)

lm5 <- lm(ngirls~ genold + white + party +female+age + Agesqr + srvlng+ Srvlngsqr+ rgroup+ region, data = Combinedtable[Combinedtable$repub==0,])
coelm5<- summary(lm5)$coefficients[2,]
print(coelm5)

lm6 <- lm(totchi~ genold + white + party +female+age + Agesqr + srvlng+ Srvlngsqr+ rgroup+ region, data = Combinedtable[Combinedtable$repub==0,])
coelm6<- summary(lm6)$coefficients[2,]
print(coelm6)
```

```
















